Honey Bee Colonies Impacted by Varroa, American Fouldbrood and Global Warming

### 2024-08-01 manuscript-exercise/manuscript_final-2.qmd
2nd HTML

![](images/dead-bees-hive-colony-collapse-600nw-2289939105.webp){width="679"}

To cite other work (important everywhere, but likely happens first in
introduction), make sure your references are in the bibtex file
specified in the YAML header above and have the right bibtex key. Then
you can include like this:

@@

@@

>>>>

![](images/dead-bees-hive-colony-collapse-600nw-2289939105.webp){width="679"}
#Citation section
To cite other work (important everywhere, but likely happens first in
introduction), make sure your references are in the bibtex file
specified in the YAML header above and have the right bibtex key. Then
you can include like this:

@@

#Here are the BibTex entries for citations:

Using this in RMarkdown:
#Make sure to save these entries in a file names'reference.bib' and include it in your R Markdown document like this:

@@

#Citations
```{r}
library(knitr)
```
